PMean: Examining relationships in R

### 2021-11-16 text/15/relationships-in-r.Rmd
Work on 15/relationships-in-r.Rmd
Added how-many-pages.md

```{r}
fn <- "http://lib.stat.cmu.edu/DASL/Datafiles/homedat.html"
h0 <- readLines(fn)
n <- length(h0)
print(n)
```

    ## [1] 165

```{r}
head(h0)
```

```{r}
tail(h0)
```

```{r}
the.data.line <- grep("The Data:",h0)
print(the.data.line)
```

```{r}
h1 <- h0[(the.data.line+4):(n-1)]
head(h1)
```

```{r}
tail(h1)
```

```{r}
h2 <- strsplit(h1,"\t")
head(h2)
```

```{r}
tail(h2)
```

```{r}
h3 <- as.numeric(unlist(h2))
```

```{r}
head(h3)
```

```{r}
tail(h3)
```

```{r}
h4 <- matrix(h3,ncol=8,byrow=TRUE)
head(h4)
```

```{r}
tail(h4)
```

```{r}
var.names.line <- the.data.line+2
print(h0[var.names.line])
```

```{r}
var.names <- strsplit(h0[var.names.line]," ")
print(var.names)
```

```{r}
var.names <- unlist(var.names)
print(var.names)
```

```{r}
var.names <- var.names[nchar(var.names)>0]
print(var.names)
```

```{r}
var.names <- tolower(var.names)
print(var.names)
```

```{r}
dimnames(h4)[[2]] <- var.names
head(h4)
```

```{r}
tail(h4)
```

```{r}
h5 <- data.frame(h4)
head(h5)
```

```{r}
tail(h5)
```

@@

```{r}
plot(h5sqft,h5$price)
lines(lowess(h5price~h5$sqft))
```

```{r}
plot(h5age,h5$price)
sb <- is.finite(h5age)
lines(lowess(h5price[sb]~h5$age[sb]))
```

@@

```{r}
cor(h5[,c("price","sqft","age")],use="pairwise.complete.obs")
```

@@

```{r}
round(cor(h5[,c("price","sqft","age")],use="pairwise.complete.obs"),1)
```

@@

```{r}
boxplot(h5price~h5$feats)
```

```{r}
boxplot(h5price~h5$ne)
```

```{r}
boxplot(h5price~h5$cust)
```

```{r}
boxplot(h5price~h5$cor)
```

@@

```{r}
plot(h5price,h5$ne)
lines(lowess(h5ne~h5$price))
```

```{r}
plot(h5price,h5$cust)
lines(lowess(h5cust~h5$price))
```

```{r}
plot(h5price,h5$cor)
lines(lowess(h5cor~h5$price))
```

@@

```{r}
round(cor(h5[,c("ne","cust","cor")],h5price),1)
```

>>>>

```{r}
suppressMessages(suppressWarnings(library(tidyverse)))
fn <- "https://raw.githubusercontent.com/pmean/introduction-to-SAS/master/data/housing.txt"
home <- read_tsv(fn, na=".")
home
```

@@

```{r}
plot(home$sqft,home$price)
lines(lowess(home$price~home$sqft))
```

```{r}
sb <- is.finite(home$age)
plot(home$age[sb],home$price[sb])
lines(lowess(home$price[sb]~home$age[sb]))
```

@@

```{r}
cor(home[,c("price","sqft","age")],use="pairwise.complete.obs")
```

@@

```{r}
round(cor(home[,c("price","sqft","age")],use="pairwise.complete.obs"),1)
```

@@

```{r}
boxplot(home$price~home$features)
```

```{r}
boxplot(home$price~home$northeast)
```

```{r}
boxplot(home$price~home$custom_build)
```

```{r}
boxplot(home$price~home$corner_lot)
```

@@

```{r}
plot(home$price,home$northeast)
lines(lowess(home$northeast~home$price))
```

```{r}
plot(home$price,home$custom_build)
lines(lowess(home$custom_build~home$price))
```

```{r}
plot(home$price,home$corner_lot)
lines(lowess(home$corner_lot~home$price))
```

@@

```{r}
round(cor(home[,c("northeast","custom_build","corner_lot")],home$price),1)
```
